\LARGE \bf The Thymio robot, open source hardware for formal education

### 2016-03-23 paper_ram.tex
draft

\subsection{Validated positive results}

@@

XXXXXXXXXXXXXXXXXX

@@

\begin{table}
\begin{tabularx}{\columnwidth}{@{}lll@{}}
\toprule
School & School type & Town in Switzerland \\
\midrule
HEPL (several units) & Teacher training & Lausanne  \\
EP Cossonay-Penthalaz & Primary school & Penthalaz  \\
EPS Ecublens & Primary and Secondary & Ecublens  \\
Collège de Vevey & Secondary & Vevey  \\
Collège Sainte Croix & Secondary & Fribourg  \\
Fondation de Verdeil & Specialized school & Lausanne  \\
Gymnase de Beaulieu & Baccalaureate school & Lausanne  \\
Gymnase de Provence & Baccalaureate school & Lausanne  \\
Lycée Blaise-Cendras & Baccalaureate school & La Chaux-de-Fonds  \\
edurobot.ch & Network of teachers & Vaud  \\
\bottomrule
\end{tabularx}
\caption{Schools and groups of teachers who develop educational material for the Thymio.}
\label{tbl:schools}
\end{table}

>>>>

\subsection{Validated added value of open source hardware}

@@

XXXXXXXXXXXXXXXXXX what is behind this line is historical....

@@
